---
title: "Correlation between Tweets and Stock Markets"
author: "Amy Lee"
date: "8/13/2021"
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::knit_hooks$set(document = function(x){
#  gsub("```\n*```r*\n*", "", x)
#})
```

#### Used Packages

```{r message=FALSE, warning=FALSE}
library(dplyr)
```
```{r message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
mymachine="/Users/jungsoolee/Documents/Git/Effect\ of\ tweets\ on\ stock\ prices"
```

# Introduction

While I was looking for an interesting project to work on, I came across a Kaggle post called"Tweets about the Top Companies from 2015 and 2020".
(link : https://www.kaggle.com/omermetinn/tweets-about-the-top-companies-from-2015-to-2020)

It includes three datasets.
  
```{r message=FALSE, warning=FALSE}
twt_to_cmpy=read.csv(paste(mymachine,'/archive/Company_Tweet.csv', sep=""))
stk=read.csv(paste(mymachine,'/archive/CompanyValues.csv', sep=''))
twt=read.csv(paste(mymachine,'/archive/Tweet.csv', sep=''))
```

Using these datasets, I intend to analyze the correlation between Tweets and company's stock prices.


## Exploratory Analysis

### 1. Datasets
#### Company_Tweet dataset
```{r results = 'hold'}
str(twt_to_cmpy)
paste("number of distinct tweets =", n_distinct(twt_to_cmpy$tweet_id))
paste("company being referred =", paste(unique(twt_to_cmpy$ticker_symbol), collapse=", "))
paste("number of NA in tweet_id =", sum(is.na(twt_to_cmpy$tweet_id)))
paste("number of NA in ticker_symbol =", sum(is.na(twt_to_cmpy$ticker_symbol)))
```

This data set contains two columns. 
And based on the setup, it seems to show which tweet posts are affecting which company.

```{r}
twt_to_cmpy%>%
  group_by(tweet_id) %>%
  summarize(Referred_Company_Count=n_distinct(ticker_symbol)) %>%
  count(Referred_Company_Count)
  #group_by(Referred_Company_Count) %>%
  #summarize(n_occurrence=count(Referred_Company_Count))
  #arrange(desc(Referred_Company_Count)) %>% #sort(Referred_Company_Count, decreasing=TRUE) %>%
  #head(20)
```









